\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-30 paper.tex
Update on Overleaf.

Figure~\ref{plan_hatp2} illustrates such a socially-optimised plan where the
\emph{no wasted time} social rule is applied: compared to the plan depicted in
Figure~\ref{plan_hatp1}, the robot first moves the bottle so that the human can
immediately take it and put it into the bin, thus removing the human idle time.
The resulting shared plan is considered better than the one depicted on
Figure~\ref{plan_hatp1} according to a global evaluation of the costs and rules.

@@

One direction that we would like to further investigate is how to account for
situations where divergent beliefs appear between the human and the robot.
Preliminary results have been published in~\cite{warnier2012when}.

>>>>

Figure~\ref{plan_hatp2} illustrates such a socially-optimised plan where the
\emph{no wasted time} social rule is applied: compared to the plan depicted in
Figure~\ref{plan_hatp1}, the robot first moves the bottle so that the human can
immediately take it and put it into the bin, thus reducing the human idle time.
The resulting shared plan is considered better than the one depicted on
Figure~\ref{plan_hatp1} according to a global evaluation of the costs and rules.

@@

One direction that we would like to further investigate is how to account for
situations where divergent beliefs appear between the human and the robot.
Some preliminary results have been presented 
in~\cite{warnier2012when,milliez2014framework}  where we consider
divergent beliefs about the state of the world, and
in~\cite{devin2016implemented} where the robot is able to deal with
divergent beliefs related to the state of the task.
